---
title: "FB_ABT_unload_final_2025.12"
output: html_document
date: "2025-12-06"
---

# Representative analysis workflow

This public script is the entrypoint for the representative analysis workflow used in the public repository.

`Neonatal Intensive Care Unit Exposures Reprogram Microbiome-Metabolome Trajectories and Modulate Host Calprotectin in Preterm Infants: A Longitudinal Multi-omics Study`

The code has been split into focused analysis modules and compact results-oriented workflow scripts so that external readers can review either the method blocks or the manuscript-aligned analysis sections. Internal study tables can be mapped to standardized public-facing column names before analysis.

```{r}
module_dir <- if (dir.exists("R")) "R" else file.path("code", "R")
module_files <- c(
  "00_setup.R",
  "01_data_standardization.R",
  "02_multivariate_analysis.R",
  "03_mixed_models.R",
  "04_interomics_network.R",
  "05_mediation_sensitivity.R"
)

for (module_file in module_files) {
  source(file.path(module_dir, module_file), local = globalenv())
}
```

# Module structure

- `R/00_setup.R`: package loading, plotting theme, color palette
- `R/01_data_standardization.R`: public-facing column mapping and table standardization
- `R/02_multivariate_analysis.R`: composition plotting, PERMANOVA, dbRDA
- `R/03_mixed_models.R`: adjusted mixed-effects models and heatmap summaries
- `R/04_interomics_network.R`: Procrustes summaries and MetaNet inter-omics network construction
- `R/05_mediation_sensitivity.R`: conservative infant-level mediation sensitivity analysis

# Manuscript-oriented workflow scripts

- `workflows/01_preterm_gut_overview.R`: Figure 1 / early colonization overview
- `workflows/02_nicu_exposures_microbiome.R`: Figure 2 / NICU exposures and microbiome structure
- `workflows/03_antibiotic_regimen_effects.R`: Figure 3 / regimen-specific antibiotic effects
- `workflows/04_metabolome_interomics.R`: Figure 4 / metabolome and inter-omics integration
- `workflows/05_calprotectin_axis.R`: Figure 5 / calprotectin-associated analyses and conservative mediation sensitivity

# Notes on release scope

This public workflow focuses on analytical components that can be documented clearly and defended directly from the released code.

Module-based metabolite analyses in the internal study workflow relied on locked eigengene objects generated during the project analysis. Those internal objects are not rebuilt here in order to avoid presenting a weaker ad hoc reconstruction as the original study pipeline.

# Example analysis outline

```{r}
# Example: standardize the main analysis table to public-facing column names.
# Replace the placeholder source column names below with the names used in your local tables.
#
# study_table <- standardize_study_table(
#   raw_study_table,
#   sample_id_col = "your_sample_identifier",
#   infant_id_col = "your_infant_identifier",
#   postnatal_age_col = "your_postnatal_age_column",
#   gestational_age_col = "your_gestational_age_column",
#   birth_weight_col = "your_birth_weight_column",
#   sex_col = "your_sex_column",
#   delivery_mode_col = "your_delivery_mode_column",
#   additional_mapping = c(
#     antibiotic_exposure_ratio_1w = "your_one_week_antibiotic_ratio_column",
#     antibiotic_exposure_ratio_2w = "your_two_week_antibiotic_ratio_column"
#   )
# )
#
# Primary covariates used across adjusted models:
# primary_covariates <- c(
#   "delivery_mode",
#   "gestational_age_weeks",
#   "birth_weight_g",
#   "sex",
#   "multiple_gestation",
#   "prenatal_antibiotics",
#   "apgar_5min",
#   "postnatal_age_days",
#   "breastmilk_exposure_ratio_total",
#   "formula_exposure_ratio_total",
#   "antibiotic_exposure_ratio_total",
#   "antifungal_exposure_ratio_total",
#   "central_line_ratio_total",
#   "invasive_ventilation_ratio_total",
#   "probiotics_ratio_total",
#   "ppi_ratio_total",
#   "rbc_transfusion_ratio_total"
# )
#
# Microbiome PERMANOVA:
# microbiome_permanova <- run_permanova_summary(
#   distance_matrix = microbiome_bray_distance,
#   metadata = study_table,
#   variables = primary_covariates
# )
#
# Adjusted mixed-effects model for a single exposure:
# antibiotic_model <- fit_adjusted_mixed_model(
#   data = study_table,
#   outcome = "microbial_load_log10",
#   exposure = "antibiotic_exposure_ratio_total",
#   covariates = setdiff(primary_covariates, "antibiotic_exposure_ratio_total"),
#   subject_id_col = "infant_id",
#   rescale_columns = c("postnatal_age_days", "antibiotic_exposure_ratio_total"),
#   rescale_method = "minmax"
# )
#
# Inter-omics network:
# network_result <- build_metanet_interomics_network(
#   microbiome_matrix = genus_abundance_matrix,
#   metabolite_matrix = metabolite_matrix
# )
#
# Conservative subject-level mediation sensitivity analysis:
# mediation_result <- run_subject_level_mediation_sensitivity(
#   data = study_table,
#   exposure = "antibiotic_exposure_ratio_total",
#   mediator = "clostridium_sensu_stricto_1_abundance",
#   outcome = "fecal_calprotectin_log",
#   covariates = c("postnatal_age_days"),
#   subject_id_col = "infant_id",
#   age_col = "postnatal_age_days",
#   min_age_days = 14
# )
```
