---
title: "FB_ABT_unload_final_2025.12"
output: html_document
date: "2025-12-06"
---

# Representative analysis workflow

This public script provides a conservative, manuscript-matched workflow for the main analyses reported in:

`Neonatal Intensive Care Unit Exposures Reprogram Microbiome-Metabolome Trajectories and Modulate Host Calprotectin in Preterm Infants: A Longitudinal Multi-omics Study`

The aim of this release is clarity and methodological fidelity rather than full internal pipeline reproduction. Functions are written around standardized public-facing column names. Internal study tables can be mapped to these names before analysis.

```{r}
# ------------------------------------------------------------------------------
# 0. Setup
# ------------------------------------------------------------------------------
if (!requireNamespace("pacman", quietly = TRUE)) {
  install.packages("pacman")
}

pacman::p_load(
  dplyr,
  tidyr,
  ggplot2,
  forcats,
  vegan,
  nlme,
  openxlsx,
  ggrepel,
  pheatmap,
  scales,
  mediation
)

set.seed(123)

theme_publication <- theme_classic() +
  theme(
    axis.text = element_text(color = "black", size = 10),
    axis.title = element_text(color = "black", size = 11, face = "bold"),
    legend.title = element_text(color = "black", face = "bold"),
    legend.text = element_text(color = "black"),
    strip.background = element_blank(),
    plot.title = element_text(hjust = 0.5, face = "bold")
  )

family_palette <- c(
  "Enterobacteriaceae" = "#C0392B",
  "Enterococcaceae" = "#A04000",
  "Staphylococcaceae" = "#F1C40F",
  "Clostridiaceae" = "#E67E22",
  "Bifidobacteriaceae" = "#8E44AD",
  "Veillonellaceae" = "#2C3E50",
  "Streptococcaceae" = "#E74C3C",
  "Other" = "grey80"
)

# ------------------------------------------------------------------------------
# 1. Data standardization
# ------------------------------------------------------------------------------
rename_present <- function(data, mapping) {
  mapping <- mapping[!is.na(mapping)]
  present_mapping <- mapping[unname(mapping) %in% colnames(data)]

  if (length(present_mapping) == 0) {
    return(data)
  }

  dplyr::rename(
    data,
    !!!rlang::set_names(rlang::syms(unname(present_mapping)), names(present_mapping))
  )
}

first_non_missing <- function(x) {
  values <- x[!is.na(x)]
  if (length(values) == 0) {
    return(NA)
  }
  values[[1]]
}

recode_binary_flag <- function(x) {
  dplyr::case_when(
    x %in% c("T", "Yes", "YES", "True", "true", 1) ~ "Yes",
    x %in% c("F", "No", "NO", "False", "false", 0) ~ "No",
    TRUE ~ as.character(x)
  )
}

recode_delivery_mode <- function(x) {
  dplyr::case_when(
    x %in% c("VD", "Vaginal") ~ "Vaginal",
    x %in% c("CS", "C-section", "Cesarean") ~ "C-section",
    TRUE ~ as.character(x)
  )
}

recode_sex <- function(x) {
  dplyr::case_when(
    x %in% c("M", "Male") ~ "Male",
    x %in% c("F", "Female") ~ "Female",
    TRUE ~ as.character(x)
  )
}

standardize_study_table <- function(
  data,
  sample_id_col = "sample_id",
  infant_id_col = "infant_id",
  postnatal_age_col = "postnatal_age_days",
  gestational_age_col = "gestational_age_weeks",
  birth_weight_col = "birth_weight_g",
  sex_col = "sex",
  delivery_mode_col = "delivery_mode",
  multiple_gestation_col = "multiple_gestation",
  prenatal_antibiotic_col = "prenatal_antibiotics",
  apgar5_col = "apgar_5min",
  breastmilk_ratio_total_col = "breastmilk_exposure_ratio_total",
  formula_ratio_total_col = "formula_exposure_ratio_total",
  antibiotic_ratio_total_col = "antibiotic_exposure_ratio_total",
  antifungal_ratio_total_col = "antifungal_exposure_ratio_total",
  invasive_ventilation_ratio_total_col = "invasive_ventilation_ratio_total",
  central_line_ratio_total_col = "central_line_ratio_total",
  probiotics_ratio_total_col = "probiotics_ratio_total",
  ppi_ratio_total_col = "ppi_ratio_total",
  rbc_transfusion_ratio_total_col = "rbc_transfusion_ratio_total",
  microbial_load_log_col = "microbial_load_log10",
  calprotectin_log_col = "fecal_calprotectin_log",
  additional_mapping = NULL
) {
  base_mapping <- c(
    sample_id = sample_id_col,
    infant_id = infant_id_col,
    postnatal_age_days = postnatal_age_col,
    gestational_age_weeks = gestational_age_col,
    birth_weight_g = birth_weight_col,
    sex = sex_col,
    delivery_mode = delivery_mode_col,
    multiple_gestation = multiple_gestation_col,
    prenatal_antibiotics = prenatal_antibiotic_col,
    apgar_5min = apgar5_col,
    breastmilk_exposure_ratio_total = breastmilk_ratio_total_col,
    formula_exposure_ratio_total = formula_ratio_total_col,
    antibiotic_exposure_ratio_total = antibiotic_ratio_total_col,
    antifungal_exposure_ratio_total = antifungal_ratio_total_col,
    invasive_ventilation_ratio_total = invasive_ventilation_ratio_total_col,
    central_line_ratio_total = central_line_ratio_total_col,
    probiotics_ratio_total = probiotics_ratio_total_col,
    ppi_ratio_total = ppi_ratio_total_col,
    rbc_transfusion_ratio_total = rbc_transfusion_ratio_total_col,
    microbial_load_log10 = microbial_load_log_col,
    fecal_calprotectin_log = calprotectin_log_col
  )

  if (!is.null(additional_mapping)) {
    base_mapping <- c(base_mapping, additional_mapping)
  }

  data_standardized <- data %>%
    rename_present(base_mapping)

  stopifnot("sample_id" %in% colnames(data_standardized))
  stopifnot("infant_id" %in% colnames(data_standardized))

  data_standardized <- data_standardized %>%
    distinct(sample_id, .keep_all = TRUE)

  if ("sex" %in% colnames(data_standardized)) {
    data_standardized <- data_standardized %>%
      mutate(sex = factor(recode_sex(sex), levels = c("Male", "Female")))
  }

  if ("delivery_mode" %in% colnames(data_standardized)) {
    data_standardized <- data_standardized %>%
      mutate(delivery_mode = factor(recode_delivery_mode(delivery_mode), levels = c("Vaginal", "C-section")))
  }

  if ("prenatal_antibiotics" %in% colnames(data_standardized)) {
    data_standardized <- data_standardized %>%
      mutate(prenatal_antibiotics = factor(recode_binary_flag(prenatal_antibiotics), levels = c("No", "Yes")))
  }

  if ("multiple_gestation" %in% colnames(data_standardized)) {
    data_standardized <- data_standardized %>%
      mutate(multiple_gestation = factor(recode_binary_flag(multiple_gestation), levels = c("No", "Yes")))
  }

  numeric_columns <- intersect(
    c(
      "postnatal_age_days",
      "gestational_age_weeks",
      "birth_weight_g",
      "apgar_5min",
      "breastmilk_exposure_ratio_total",
      "formula_exposure_ratio_total",
      "antibiotic_exposure_ratio_total",
      "antifungal_exposure_ratio_total",
      "invasive_ventilation_ratio_total",
      "central_line_ratio_total",
      "probiotics_ratio_total",
      "ppi_ratio_total",
      "rbc_transfusion_ratio_total",
      "microbial_load_log10",
      "fecal_calprotectin_log"
    ),
    colnames(data_standardized)
  )

  data_standardized %>%
    mutate(across(all_of(numeric_columns), as.numeric))
}

rescale_numeric_columns <- function(data, columns, method = c("none", "zscore", "minmax")) {
  method <- match.arg(method)
  columns <- intersect(columns, colnames(data))

  if (length(columns) == 0 || method == "none") {
    return(data)
  }

  if (method == "zscore") {
    data %>%
      mutate(across(all_of(columns), ~ as.numeric(scale(.x))))
  } else {
    data %>%
      mutate(
        across(
          all_of(columns),
          ~ (.x - min(.x, na.rm = TRUE)) / (max(.x, na.rm = TRUE) - min(.x, na.rm = TRUE))
        )
      )
  }
}

available_columns <- function(data, columns) {
  intersect(columns, colnames(data))
}

# ------------------------------------------------------------------------------
# 2. Core visualization helpers
# ------------------------------------------------------------------------------
plot_ordered_composition_bar <- function(data_long, abundance_col, family_col = "Family") {
  ggplot(
    data_long,
    aes(
      x = fct_reorder(sample_id, microbial_load_log10),
      y = .data[[abundance_col]],
      fill = .data[[family_col]]
    )
  ) +
    geom_col(width = 1) +
    scale_fill_manual(values = family_palette) +
    labs(x = "Samples", y = abundance_col) +
    theme_publication +
    theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
}

plot_effect_size_forest <- function(results_table, label_col = "Variable", effect_col = "Effect",
                                    ci_low_col = "CI_low", ci_high_col = "CI_high",
                                    y_label = "Normalized effect size") {
  ggplot(results_table, aes(x = forcats::fct_reorder(.data[[label_col]], .data[[effect_col]]),
                            y = .data[[effect_col]])) +
    geom_point(size = 2) +
    geom_errorbar(aes(ymin = .data[[ci_low_col]], ymax = .data[[ci_high_col]]), width = 0.2) +
    coord_flip() +
    geom_hline(yintercept = 0, color = "red4", linetype = "dashed", alpha = 0.7) +
    labs(x = NULL, y = y_label) +
    theme_publication
}

# ------------------------------------------------------------------------------
# 3. PERMANOVA and dbRDA
# ------------------------------------------------------------------------------
as_distance_matrix <- function(x, method) {
  if (inherits(x, "dist")) {
    return(x)
  }
  vegan::vegdist(as.matrix(x), method = method)
}

align_metadata_to_distance <- function(distance_matrix, metadata, sample_id_col = "sample_id") {
  sample_ids <- labels(distance_matrix)
  metadata %>%
    filter(.data[[sample_id_col]] %in% sample_ids) %>%
    tibble::column_to_rownames(sample_id_col) %>%
    .[sample_ids, , drop = FALSE]
}

run_permanova_summary <- function(distance_matrix, metadata, variables,
                                  sample_id_col = "sample_id",
                                  permutations = 2000,
                                  p_adjust_method = "fdr") {
  distance_matrix <- as_distance_matrix(distance_matrix, method = "bray")
  metadata_aligned <- align_metadata_to_distance(distance_matrix, metadata, sample_id_col = sample_id_col)

  model_variables <- available_columns(metadata_aligned, variables)
  stopifnot(length(model_variables) > 0)

  formula_text <- paste("distance_matrix ~", paste(model_variables, collapse = " + "))
  permanova_result <- adonis2(
    as.formula(formula_text),
    data = metadata_aligned,
    permutations = permutations,
    by = "margin"
  )

  as.data.frame(permanova_result) %>%
    tibble::rownames_to_column("Variable") %>%
    filter(!Variable %in% c("Total", "Residual")) %>%
    mutate(P_adj = p.adjust(`Pr(>F)`, method = p_adjust_method)) %>%
    arrange(desc(R2))
}

run_dbrda_summary <- function(feature_matrix, metadata, variables,
                              sample_id_col = "sample_id",
                              distance_method = "bray",
                              permutations = 2000,
                              p_adjust_method = "fdr") {
  feature_matrix <- as.data.frame(feature_matrix)
  metadata_aligned <- metadata %>%
    filter(.data[[sample_id_col]] %in% rownames(feature_matrix)) %>%
    tibble::column_to_rownames(sample_id_col)
  metadata_aligned <- metadata_aligned[rownames(feature_matrix), , drop = FALSE]

  model_variables <- available_columns(metadata_aligned, variables)
  stopifnot(length(model_variables) > 0)

  formula_text <- paste("feature_matrix ~", paste(model_variables, collapse = " + "))
  dbrda_model <- capscale(as.formula(formula_text), data = metadata_aligned, dist = distance_method)

  anova_table <- anova(dbrda_model, by = "margin", permutations = permutations) %>%
    as.data.frame() %>%
    tibble::rownames_to_column("Variable") %>%
    filter(Variable != "Residual") %>%
    mutate(P_adj = p.adjust(`Pr(>F)`, method = p_adjust_method))

  list(
    model = dbrda_model,
    anova_table = anova_table,
    sites = as.data.frame(scores(dbrda_model, display = "sites", choices = 1:2)) %>%
      tibble::rownames_to_column("sample_id"),
    vectors = as.data.frame(scores(dbrda_model, display = "bp", choices = 1:2)) %>%
      tibble::rownames_to_column("Variable")
  )
}

plot_dbrda_biplot <- function(dbrda_result, metadata,
                              fill_col = "postnatal_age_days",
                              arrow_multiplier = 3) {
  significant_vectors <- dbrda_result$vectors %>%
    left_join(dbrda_result$anova_table %>% select(Variable, P_adj), by = "Variable") %>%
    filter(P_adj < 0.1)

  site_table <- dbrda_result$sites %>%
    left_join(metadata, by = "sample_id")

  ggplot() +
    geom_point(
      data = site_table,
      aes(x = CAP1, y = CAP2, fill = .data[[fill_col]]),
      shape = 21,
      size = 2.5,
      alpha = 0.8
    ) +
    geom_segment(
      data = significant_vectors,
      aes(x = 0, y = 0, xend = CAP1 * arrow_multiplier, yend = CAP2 * arrow_multiplier),
      arrow = arrow(length = unit(0.2, "cm")),
      color = "black"
    ) +
    geom_text_repel(
      data = significant_vectors,
      aes(x = CAP1 * arrow_multiplier * 1.1, y = CAP2 * arrow_multiplier * 1.1, label = Variable),
      size = 3
    ) +
    scale_fill_gradient(low = "grey85", high = "#2C7FB8") +
    labs(x = "dbRDA1", y = "dbRDA2") +
    theme_publication
}

# ------------------------------------------------------------------------------
# 4. Mixed-effects models
# ------------------------------------------------------------------------------
fit_adjusted_mixed_model <- function(data, outcome, exposure, covariates = NULL,
                                     subject_id_col = "infant_id",
                                     rescale_columns = NULL,
                                     rescale_method = c("none", "minmax", "zscore")) {
  model_columns <- unique(c(subject_id_col, outcome, exposure, covariates))
  model_columns <- available_columns(data, model_columns)
  model_data <- data %>%
    select(all_of(model_columns)) %>%
    tidyr::drop_na(all_of(c(outcome, exposure, subject_id_col)))

  rescale_targets <- if (is.null(rescale_columns)) character(0) else rescale_columns
  model_data <- rescale_numeric_columns(
    model_data,
    columns = intersect(rescale_targets, colnames(model_data)),
    method = match.arg(rescale_method)
  )

  rhs_terms <- c(exposure, available_columns(model_data, covariates))
  model_formula <- as.formula(paste(outcome, "~", paste(rhs_terms, collapse = " + ")))

  nlme::lme(
    fixed = model_formula,
    random = as.formula(paste("~1|", subject_id_col)),
    data = model_data,
    na.action = na.omit
  )
}

extract_model_results <- function(model_object) {
  as.data.frame(summary(model_object)$tTable) %>%
    tibble::rownames_to_column("Variable") %>%
    rename(
      Effect = Value,
      Standard_Error = Std.Error,
      Degrees_of_Freedom = DF,
      T_value = `t-value`,
      P_value = `p-value`
    ) %>%
    mutate(
      CI_low = Effect - 1.96 * Standard_Error,
      CI_high = Effect + 1.96 * Standard_Error
    )
}

run_heatmap_models <- function(data, outcomes, focal_exposure, covariates = NULL,
                               subject_id_col = "infant_id",
                               rescale_columns = NULL,
                               rescale_method = c("none", "minmax", "zscore")) {
  results <- lapply(outcomes, function(outcome_name) {
    fitted_model <- fit_adjusted_mixed_model(
      data = data,
      outcome = outcome_name,
      exposure = focal_exposure,
      covariates = covariates,
      subject_id_col = subject_id_col,
      rescale_columns = rescale_columns,
      rescale_method = match.arg(rescale_method)
    )

    extract_model_results(fitted_model) %>%
      filter(Variable == focal_exposure) %>%
      transmute(
        Outcome = outcome_name,
        Exposure = focal_exposure,
        Effect,
        P_value,
        CI_low,
        CI_high
      )
  })

  bind_rows(results)
}

plot_model_heatmap <- function(results_table, value_col = "Effect") {
  heatmap_matrix <- results_table %>%
    select(Outcome, Exposure, .data[[value_col]]) %>%
    pivot_wider(names_from = Exposure, values_from = .data[[value_col]]) %>%
    tibble::column_to_rownames("Outcome") %>%
    as.matrix()

  pheatmap::pheatmap(
    heatmap_matrix,
    color = colorRampPalette(c("navy", "white", "firebrick3"))(100),
    cluster_rows = FALSE,
    cluster_cols = FALSE,
    border_color = "grey90"
  )
}

# ------------------------------------------------------------------------------
# 5. Procrustes and network analysis
# ------------------------------------------------------------------------------
run_procrustes_summary <- function(microbiome_distance, metabolite_distance,
                                   permutations = 2000) {
  microbiome_distance <- as_distance_matrix(microbiome_distance, method = "bray")
  metabolite_distance <- as_distance_matrix(metabolite_distance, method = "euclidean")

  shared_ids <- intersect(labels(microbiome_distance), labels(metabolite_distance))
  microbiome_distance <- as.dist(as.matrix(microbiome_distance)[shared_ids, shared_ids])
  metabolite_distance <- as.dist(as.matrix(metabolite_distance)[shared_ids, shared_ids])

  protest_result <- protest(
    microbiome_distance,
    metabolite_distance,
    scores = "sites",
    permutations = permutations
  )

  list(
    test = protest_result,
    plot_table = data.frame(
      sample_id = shared_ids,
      microbiome_axis1 = protest_result$X[, 1],
      microbiome_axis2 = protest_result$X[, 2],
      metabolite_axis1 = protest_result$Yrot[, 1],
      metabolite_axis2 = protest_result$Yrot[, 2]
    )
  )
}

plot_procrustes_summary <- function(procrustes_result) {
  ggplot(procrustes_result$plot_table) +
    geom_segment(
      aes(
        x = microbiome_axis1,
        y = microbiome_axis2,
        xend = metabolite_axis1,
        yend = metabolite_axis2
      ),
      color = "grey80",
      alpha = 0.5
    ) +
    geom_point(aes(x = microbiome_axis1, y = microbiome_axis2), color = "#E64B35FF", size = 2) +
    geom_point(aes(x = metabolite_axis1, y = metabolite_axis2), color = "#4DBBD5FF", size = 2) +
    annotate(
      "text",
      x = min(procrustes_result$plot_table$microbiome_axis1),
      y = max(procrustes_result$plot_table$microbiome_axis2),
      label = paste0(
        "Procrustes t0 = ",
        round(procrustes_result$test$t0, 3),
        "\nP = ",
        procrustes_result$test$signif
      )
    ) +
    labs(x = "Axis 1", y = "Axis 2") +
    theme_publication
}

build_metanet_interomics_network <- function(microbiome_matrix, metabolite_matrix,
                                             r_threshold = 0.3,
                                             p_threshold = 0.01,
                                             use_p_adj = TRUE,
                                             delete_single = TRUE) {
  if (!requireNamespace("MetaNet", quietly = TRUE)) {
    stop("MetaNet package is required for network analysis.")
  }

  shared_ids <- intersect(rownames(microbiome_matrix), rownames(metabolite_matrix))
  microbiome_matrix <- as.data.frame(microbiome_matrix[shared_ids, , drop = FALSE])
  metabolite_matrix <- as.data.frame(metabolite_matrix[shared_ids, , drop = FALSE])

  network_object <- MetaNet::multi_net_build(
    list(Microbiome = microbiome_matrix, Metabolome = metabolite_matrix),
    r_threshold = r_threshold,
    p_threshold = p_threshold,
    use_p_adj = use_p_adj,
    delete_single = delete_single
  )

  list(
    network = network_object,
    edge_table = as.data.frame(MetaNet::get_e(network_object))
  )
}

# ------------------------------------------------------------------------------
# 6. Conservative mediation sensitivity analysis
# ------------------------------------------------------------------------------
run_subject_level_mediation_sensitivity <- function(data, exposure, mediator, outcome,
                                                    covariates = NULL,
                                                    subject_id_col = "infant_id",
                                                    age_col = "postnatal_age_days",
                                                    min_age_days = NULL,
                                                    sims = 1000) {
  model_columns <- unique(c(subject_id_col, exposure, mediator, outcome, covariates, age_col))
  model_columns <- available_columns(data, model_columns)
  model_data <- data %>% select(all_of(model_columns))

  if (!is.null(min_age_days) && age_col %in% colnames(model_data)) {
    model_data <- model_data %>% filter(.data[[age_col]] >= min_age_days)
  }

  subject_level_data <- model_data %>%
    group_by(.data[[subject_id_col]]) %>%
    summarise(
      across(
        -all_of(subject_id_col),
        ~ if (is.numeric(.x)) median(.x, na.rm = TRUE) else first_non_missing(.x)
      ),
      .groups = "drop"
    ) %>%
    tidyr::drop_na(all_of(c(exposure, mediator, outcome)))

  mediator_model <- lm(
    as.formula(paste(mediator, "~", paste(c(exposure, available_columns(subject_level_data, covariates)), collapse = " + "))),
    data = subject_level_data
  )

  outcome_model <- lm(
    as.formula(paste(outcome, "~", paste(c(exposure, mediator, available_columns(subject_level_data, covariates)), collapse = " + "))),
    data = subject_level_data
  )

  mediation_result <- mediate(
    mediator_model,
    outcome_model,
    treat = exposure,
    mediator = mediator,
    boot = TRUE,
    sims = sims
  )

  data.frame(
    n_infants = nrow(subject_level_data),
    ACME = mediation_result$d0,
    ADE = mediation_result$z0,
    Total_Effect = mediation_result$tau.coef,
    Prop_Mediated = mediation_result$n0,
    P_ACME = mediation_result$d0.p
  )
}
```

# Notes on release scope

This representative public script focuses on the main analytical components that can be documented clearly and defended directly from the released code.

Module-based metabolite analyses in the internal study workflow relied on locked eigengene objects generated during the project analysis. Those internal objects are not rebuilt here in order to avoid presenting a weaker ad hoc reconstruction as the original study pipeline.

# Example analysis outline

```{r}
# Example: standardize the main analysis table to public-facing column names.
# Replace the placeholder source column names below with the names used in your local tables.
#
# study_table <- standardize_study_table(
#   raw_study_table,
#   sample_id_col = "your_sample_identifier",
#   infant_id_col = "your_infant_identifier",
#   postnatal_age_col = "your_postnatal_age_column",
#   gestational_age_col = "your_gestational_age_column",
#   birth_weight_col = "your_birth_weight_column",
#   sex_col = "your_sex_column",
#   delivery_mode_col = "your_delivery_mode_column",
#   additional_mapping = c(
#     antibiotic_exposure_ratio_1w = "your_one_week_antibiotic_ratio_column",
#     antibiotic_exposure_ratio_2w = "your_two_week_antibiotic_ratio_column"
#   )
# )
#
# Primary covariates used across adjusted models:
# primary_covariates <- c(
#   "delivery_mode",
#   "gestational_age_weeks",
#   "birth_weight_g",
#   "sex",
#   "multiple_gestation",
#   "prenatal_antibiotics",
#   "apgar_5min",
#   "postnatal_age_days",
#   "breastmilk_exposure_ratio_total",
#   "formula_exposure_ratio_total",
#   "antibiotic_exposure_ratio_total",
#   "antifungal_exposure_ratio_total",
#   "central_line_ratio_total",
#   "invasive_ventilation_ratio_total",
#   "probiotics_ratio_total",
#   "ppi_ratio_total",
#   "rbc_transfusion_ratio_total"
# )
#
# Microbiome PERMANOVA:
# microbiome_permanova <- run_permanova_summary(
#   distance_matrix = microbiome_bray_distance,
#   metadata = study_table,
#   variables = primary_covariates
# )
#
# Adjusted mixed-effects model for a single exposure:
# antibiotic_model <- fit_adjusted_mixed_model(
#   data = study_table,
#   outcome = "microbial_load_log10",
#   exposure = "antibiotic_exposure_ratio_total",
#   covariates = setdiff(primary_covariates, "antibiotic_exposure_ratio_total"),
#   subject_id_col = "infant_id",
#   rescale_columns = c("postnatal_age_days", "antibiotic_exposure_ratio_total"),
#   rescale_method = "minmax"
# )
#
# Inter-omics network:
# network_result <- build_metanet_interomics_network(
#   microbiome_matrix = genus_abundance_matrix,
#   metabolite_matrix = metabolite_matrix
# )
#
# Conservative subject-level mediation sensitivity analysis:
# mediation_result <- run_subject_level_mediation_sensitivity(
#   data = study_table,
#   exposure = "antibiotic_exposure_ratio_total",
#   mediator = "clostridium_sensu_stricto_1_abundance",
#   outcome = "fecal_calprotectin_log",
#   covariates = c("postnatal_age_days"),
#   subject_id_col = "infant_id",
#   age_col = "postnatal_age_days",
#   min_age_days = 14
# )
```
